Analyzing 10k Unpaired Runs
========================================================

This document outlines the analysis of the 
**unpaired** metapop simulations for the sensitivity
analysis project. 

I have already run these simulations and need
to include definitions and variable settings
here. This is work to be done.

## Set variables

```{r}
# Snowy Plover Project Directory
snpl.project.dir <- '/media/AKCAKAYA2/Projects/SnowyPlover/'
# SA Code directory
sacode.snpl <- '/home/mlammens/Dropbox/RA-FL-Shore-Birds/SensitivityAnalysis/SACode_SNPL/'
# Command to start a RAMAS Metapop simulation in R
metapop.cmd.prefix <- 'wine ~/Dropbox/RAMAS/MetapopCmd_Verbose.exe '
```

After running the *.mp simulations I have to check
to see that all of the simulations actually ran.

```{r, eval=FALSE}
# First define a list of the *.mp files to run
snpl.mp.files <- Sys.glob(paths="snpl*mp")
# Every *.mp file that successfully ran should have
# an associated scl file. So first, get all the 
# scl files
snpl.scl.files <- Sys.glob(paths="snpl*SCL")
# String replace the SCL with mp
snpl.mp.files.Done <- sub("SCL","mp",snpl.scl.files)
# Use Set Operation setdiff to get a list of the
# mp files that did not get run
snpl.mp.files.ToRun <- setdiff(snpl.mp.files,snpl.mp.files.Done)
# Run this list of *.mp files
for ( snpl in snpl.mp.files.ToRun ){
  # Concatenate metapop command
  metapop.cmd <- paste( metapop.cmd.prefix, snpl, sep="" )
  # Call Metatpop.exe
  system( metapop.cmd )  
}
```
After re-runs, extract data

```{r}
# Set working directory to be were the gentime program is
setwd( sacode.snpl )

# Make a vector of mp.files WITH full paths
snpl.mp.files.full <- paste( snpl.project.dir, 'SampleSize_10000_UNPAIRED_SA1/', snpl.mp.files, sep='' )
                             
# Name of resout.csv file
res.out.file <- '/home/mlammens/Dropbox/RA-FL-Shore-Birds/SensitivityAnalysis/Results/snpl.10000.UNPAIRED.csv'

# Call mult results function
mp.mult.results.snpl(mp.file.list=snpl.mp.files.full, 
                     out.csv=res.out.file,
                     spatial=TRUE,
                     mac=TRUE)
```

Having run the extraction, I realized that I lost
all information regarding whether the *.mp file was
associated with 2m SLR or No SLR. So I have to
run through all of the mp again, and get a vector
of that information. I can do this by doing a `grepl`
search on the kch change file name for '2M'.

```{r}
slr <- c()
for ( snpl in snpl.mp.files.full ){
  # Read the mp file
  mp <- mp.read(as.character(snpl))
  # Get the kch file names
  kch.files <- mp$mp.file$PopData_df$KchangeSt
  # classify as slr scenario or not
  is.slr <- all(grepl('2M',kch.files))
  # Add value of slr or no slr to `slr` vector
  mp.slr <- ifelse( test=is.slr, yes='SLR', no='NoSLR' )
  slr <- c( slr, mp.slr )
}
```